Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-09 thesis/chapters/ch_chapter4.tex
Final text on mixing timescales with eddy turnover and sound speed. removing one-shot TBD

We summarize the source-averaged results for all enrichment events in runs \runone E46, \runone E49, \runone E50, \runone E51, and \runone E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid). These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, solid), CGM (black, dashed) lines. In Chapter~\ref{ch:chapter3}
% \citep{Emerick2019}
we demonstrated that there was a significant difference in metal ejection fraction, $f_{\rm ej}$, for metals from AGB sources as compared to metals released in SNe. Here, we confirm that this is driven predominantly by differences in the energy of the events, and not necessarily when or where they occur in the ISM. The clear trend in Figure~\ref{ch4:fig:ISM_CGM} shows that events with higher $E_{\rm ej}$ are much more readily ejected from the disk of the galaxy, while events with lower $E_{\rm ej}$ couple poorly to the same galactic outflows.
%\textit{statement on how immediate enrichment is after events}
% By 10~Myr after the enrichment events,
The high-energy events rapidly converge on a peak $f_{\rm ej}$ within about 20~Myr of the event, with only a gradual increase towards the end of the 150~Myr as the metals in the ISM are swept up in additional outflows. The lower energy events evolve more gradually. The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej}$ ~ 0.68, which increases to 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event. To emphasize these differences, we plot each line separately in the left panel of Figure~\ref{ch4:fig:CGM_CNM}

@@

Clearly, at no point can any of these distributions be considered well-mixed within the 150~Myr simulation time. \textit{Need to fix up: This is in agreement with the understanding that the mxiing timescales should correspond to XXX, which suggests that it would take $\sim$X~Gyr (1 Gyr?) for the metals to be fully mixed}. Interestingly, however, the injection energy for a given source leaves an indelible impact on the subsequent evolution of those metals in the ISM throughout the simulation time. We demonstrate that variations in abundance spread across elements may be driven significantly by the enrichment site and its associated $E_{\rm ej}$. Metals from \runone E46 are significantly less well-mixed than their higher-energy counterparts at \runone E51 and \runone E52. Interestingly, \runone E49 behaves much more similarly to \runone E46 -- with poor mixing -- even though it is much closer in energy to the \runone E51. For what mixing does occur in the CNM for these elements, it is apparent that it happens much faster ($\sim$20~Myr) for the highest energy event than the lower energy events which take longer to plateau to a consistent value.

@@

Variations with individual events in the above results suggests that it would be challenging to make any conclusive statements about the enrichment behavior of single enrichment sources. \textbf{Go back and look again at one-shot enrichment paper} This is problematic for interpreting the chemical abundances in UFDs that are likely to have been host to just a single, exotic enrichment event. Using these observations to constrain the total nucleosynthetic yields of these sources requires implicit assumptions about how quickly metals are available in star forming gas, how homogeneously they are distributed throughout the galaxy, and what fraction are ejected from the galaxy. It is likely that none of these quantities can be determined as simple parameters based upon the feedback properties of a single enrichment source or even the global properties of a galaxy (such as $M_{\rm halo}$, $\Sigma_{\rm SFR}$, $\Sigma_{\rm gas}$). However, this study has shown that these parameters can be characterized in an averaged sense, even though the exact result is subject to substantial stochastic effects. This, combined with some mechanism to provide this stochasticity, can be used in combination with many runs of a simple galactic chemical evolution model to understand the possible outcomes for various galaxies. Developing such a model will be a powerful tool for interpreting the irregular stellar abundance patterns observed in low mass dwarf galaxies in the nearby Universe.

>>>>

We summarize the source-averaged results for all enrichment events in runs \runone E46, \runone E49, \runone E50, \runone E51, and \runone E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid). These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, solid), CGM (black, dashed) lines. In Chapter~\ref{ch:chapter3}
% \citep{Emerick2019}
we demonstrated that there was a significant difference in metal ejection fraction, $f_{\rm ej}$, for metals from AGB sources as compared to metals released in SNe. Here, we confirm that this is driven predominantly by differences in the energy of the events, and not necessarily when or where they occur in the ISM. The clear trend in Figure~\ref{ch4:fig:ISM_CGM} shows that events with higher $E_{\rm ej}$ are much more readily ejected from the disk of the galaxy, while events with lower $E_{\rm ej}$ couple poorly to the same galactic outflows.
%\textit{statement on how immediate enrichment is after events}
% By 10~Myr after the enrichment events,
The high-energy events rapidly converge on a peak $f_{\rm ej}$ within about 20~Myr of the event, with only a gradual increase towards the end of the 150~Myr as the metals in the ISM are swept up in additional outflows. The lower energy events evolve more gradually. The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej} \sim$~0.68, which increases to 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event. To emphasize these differences, we plot each line separately in the left panel of Figure~\ref{ch4:fig:CGM_CNM}

@@

Clearly, at no point can any of these distributions be considered well-mixed within the 150~Myr simulation time. Prior studies of passive scalar mixing in isothermal turbulent boxes find typical mixing timescales\footnote{Defined roughly as the time it takes for the r.m.s. abundance to equilibrate, not the time it takes to completely homogenize, which tends towards infinity.} on order of the eddy turnover timescale \citep[e.g.][]{SurPanScannapieco2014} ($t_{\rm ed}$). Typically, $t_{\rm ed}$ is defined as the relevant length scale (e.g. the diameter of our galaxy) divided by the r.m.s gas velocity. Although extending these results to multi-phase, global-galaxy simulations is non-trivial, we find typical $t_{\rm ed}$ in the CNM of $\sim$100~Myr and in the HIM of $\sim$10~Myr.\footnote{For comparison, the isothermal sound speed in these phases are $\sim$4~Gyr and $\sim$10~Myr respectively.} In order to properly evaluate the mixing timescale we would need to run each simulation for significantly longer, for several $t_{\rm ed}$.

Interestingly, the injection energy for a given source leaves an indelible impact on the subsequent evolution of those metals in the ISM throughout the simulation time. We demonstrate that variations in abundance spread across elements may be driven significantly by the enrichment site and its associated $E_{\rm ej}$. Metals from \runone E46 are significantly less well-mixed than their higher-energy counterparts at \runone E51 and \runone E52. Interestingly, \runone E49 behaves much more similarly to \runone E46 -- with poor mixing -- even though it is much closer in energy to the \runone E51. For what mixing does occur in the CNM for these elements, it is apparent that it happens much faster ($\sim$20~Myr) for the highest energy event than the lower energy events which take longer to plateau to a consistent value.

@@

Variations with individual events in the above results suggests that it would be challenging to make any conclusive statements about the enrichment behavior of single enrichment sources. This is problematic for interpreting the chemical abundances in UFDs that are likely to have been host to just a single, exotic enrichment event. Using these observations to constrain the total nucleosynthetic yields of these sources requires implicit assumptions about how quickly metals are available in star forming gas, how homogeneously they are distributed throughout the galaxy, and what fraction are ejected from the galaxy. It is likely that none of these quantities can be determined as simple parameters based upon the feedback properties of a single enrichment source or even the global properties of a galaxy (such as $M_{\rm halo}$, $\Sigma_{\rm SFR}$, $\Sigma_{\rm gas}$). However, this study has shown that these parameters can be characterized in an averaged sense, even though the exact result is subject to substantial stochastic effects. This, combined with some mechanism to provide this stochasticity, can be used in combination with many runs of a simple galactic chemical evolution model to understand the possible outcomes for various galaxies. Developing such a model will be a powerful tool for interpreting the irregular stellar abundance patterns observed in low mass dwarf galaxies in the nearby Universe.
